Linearizability Proofs Based On Forward Simulations

### 2017-01-20 draftCAV/stack.tex
started stacks

@@

>>>>

\begin{wrapfigure}{l}{6.1cm}
\vspace{-14mm}
\begin{lstlisting}
struct Node{
  int data;
  int ts;
  Node* next;
  boolean taken;
};
Node* pools[maxThreads];
int TS = 0;

void push(int x) {
  Node* n = new Node(x,MAX_INT,
                        null,false);
  n->next = pools[myTID];
  pools[myTID] = n;
  int i = TS++;
  n->ts = i;
}
int pop() {
 boolean success = false;
 int maxTS = -1;
 Node* youngest = null;
 while ( !success ) {
   maxTS = -1; youngest = null;
   for(int i = 0; i < maxThreads; i++){
     Node* n = pools[i];
     while (n->taken && n->next != null)
       n = n->next;
     if(maxTS < n->ts) {
       maxTS = n->ts; youngest = n;
     }
   }
   success=CAS(youngest->taken,false,true);
 }
 return youngest->data;
}
\end{lstlisting}
\vspace{-6mm}
\caption{Time-Stamped Stack. We assume that every statement is atomic.}
\label{fig:TimeStamped}
\vspace{-1mm}
\end{wrapfigure}
We explain the meaning of the commit points on a simplified version of the Time-Stamped Stack~\cite{DBLP:conf/popl/DoddsHK15} given in Figure~\ref{fig:TimeStamped}. This stack implementation maintains a vector of singly-linked lists, one for each thread, where list nodes contain a data value (field {\tt data}), a timestamp (field {\tt ts}), the next pointer (field {\tt next}), and a boolean flag indicating whether the node represents a value removed from the stack (field {\tt taken}). Initially, each list contains a sentinel dummy node pointing to {\tt null} with timestamp $-1$ and the flag {\tt taken} set to {\tt false}.

Pushing a value to the stack proceeds in several steps: adding a node with maximal timestamp, asking for a new timestamp (given by the value of the shared integer {\tt TS}), and updating the timestamp of the added node. Popping a value from the stack consists in traversing all the lists, finding the first element which doesn't represent a removed value (i.e., {\tt taken} is {\tt false}) in each list, and selecting the element with the maximal timestamp. A compare-and-swap (CAS) is used to set the {\tt taken} flag of this element to {\tt true}. The procedure restarts if the CAS fails.

@@

// Initially each pool[i] points to a 
// sentinel dummy node with ts = -1, 
// next = null, taken=false
